title: "WriteUp Linear Model with prediction"
author: "Hailey Watkins-Oliver"
date: "2024-04-04"
output: html_document
---

```{r setup, include=FALSE}
require(knitr)
require(tidyverse)
require(tigerstats)
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```

### Model1: SIMS~ARM
```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```

```{r}
basicNN + geom_point() + ggtitle("SIMS vs ARM")
```

This scatter plot has a positive slope going up. This shows the average amount of strength lies withing 50 and 100. What the plot describes is the relation of arm strength for the select employees.

### Numerical Results 

```{r}
cor(SIMS~ARM,data=data)
```

The numerical results confirm a positive correlation in the scatter plot of SIMS versus ARM. Higher values indicate a stronger correlation between the two. From this data, we observe a moderate relationship between them, as the value is approaching 1.

### Inferential Results 

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
